Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-10-04 Submission.Rmd
moved "Figure 5" chunk above "Figure 3 & 4" so proper numbering sequence would render
first 2 paragraphs correlation section ok

@@

library(gridExtra)
grid.arrange(b, c, a, nrow = 3)

@@

library(gridExtra)
grid.arrange(e, f, d, nrow = 3)

@@

## resource$sd

H1 states that *not everyone agrees* that a given characterisitic is a work hindrance, challenge, or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items. Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).

To provide more tangible flavor to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide support for H1, and particularly so for hindrances.

@@

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *exclusively* categorized as a resource or demand. We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix. Table 1 provides correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance. Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics *were* uniquely categorized as such. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.

@@

>>>>

## Moved up from lower location 9/30 because of Figure numbering within paper
## resource$sd

@@

library(gridExtra)
grid.arrange(b, a, c, nrow = 3)

@@

library(gridExtra)
grid.arrange(e, d, f, nrow = 3)

@@

H1 states that *not everyone agrees* that a given characterisitic is a work hindrance, challenge, or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items. Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances). These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).

To provide more context to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide support for H1, and particularly so for hindrances.

@@

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *exclusively* categorized as a resource or demand. We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix exploration. Table \@ref(tab:cortab) provides correlations among O\*NET item "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across resource, challenge, and hindrance evaluations. Here one would expect only trivial associations *across* resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.

First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.

@@

Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).

### 2025-10-04 Submission.tex
first 2 paragraphs correlation section ok

H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items. Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).

To provide more tangible flavor to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16). In sum, these results provide support for H1, and particularly so for hindrances.

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand. We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix. Table 1 provides correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance. Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics \emph{were} uniquely categorized as such. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16). Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.

@@

>>>>

H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items. Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances). These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).

To provide more context to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16). In sum, these results provide support for H1, and particularly so for hindrances.

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand. We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix exploration. Table \ref{tab:cortab} provides correlations among O*NET item ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across resource, challenge, and hindrance evaluations. Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.

First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16). Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.

@@

Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
